Women in Film

### 2017-07-17 draft_post.Rmd
Edit text a bit

example_text <- example_words %>%
    mutate(pronoun = pronouns,
           phrase = str_c(pronoun, word, sep = " ")) %>%
    pull(phrase) %>%
    map_df(function(x) all_lines %>%
               filter(nchar(text) < 140,
                      str_detect(text, x)) %>%
               sample_n(1) %>%
               select(text)) %>%
    bind_cols(example_words) %>%
    select(word, text)

>>>>

example_text <- example_words %>%
    mutate(pronoun = pronouns,
           phrase = str_c(pronoun, word, sep = " ")) %>%
    pull(phrase) %>%
    map_df(function(x) all_lines %>%
               filter(nchar(text) < 180,
                      str_detect(text, x)) %>%
               sample_n(1) %>%
               select(text)) %>%
    bind_cols(example_words) %>%
    select(word, text)
